---
title: "Problem Set 2 Causal Inference"
output:
  pdf_document: 
    latex_engine: lualatex
  html_document: default
  word_document: default
date: "2024-02-21"
---

```{r setup, include=FALSE}

rm(list = ls())

library(dagitty)
library(splitTools)
library(dplyr)
library(boot)
library(ggplot2)
library(nptest)
library(nnet)
library(twang)
library(MatchIt)
library(Hmisc)
library(DescTools)
library(mlr3misc)
library(groupdata2)

setwd("/Users/nicolocapirone/Documents/Uni/BU/Causal Inference/Problem Sets")

data <- read.csv("nhanes_bmi.csv")

covmat <- cov(subset(data[4:14]))

meanvec <- colMeans(subset(data[4:14]))

data$mdist <- mahalanobis(subset(data[4:14]), meanvec, covmat)

set.seed(70)

dataf <- fold(data = data, k = .5, num_col = "mdist", method = "n_dist")

datanf <- subset(dataf, .folds == 1, select = -c(.folds))

dataate <- subset(dataf, .folds == 2, select = -c(.folds))

rm(dataf)


```

# Estimating Propensity Score

```{r, include=TRUE}

prop_score <- glm(School_meal ~ age + I(age^2) + ChildSex + black + mexam + 
                    pir200_plus + I(pir200_plus^2) + WIC + Food_Stamp + fsdchbi 
                  + AnyIns + RefAge, data = datanf, family = "binomial")

dataate$π <- predict(prop_score, dataate, type = "response")

```

# Checking Balancing Property

A propensity score is said to satisfy the balancing property when: 
$E[\frac{A}{π(x)}Y h(x)] \approx E[h(x)], h(x) = x$

```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

#Age

ci_bal_age <- function(data,idx){
  df <- data[idx, ]
  
  bal_check <- sum((df$School_meal/df$π)*df$age)
    
  diff <- bal_check/1665 - sum(df$age)/1665

  return(diff)
  
}

boot_age <- boot(dataate, ci_bal_age, R = 1500)
suppressWarnings(
ci_age <- boot.ci(boot_age)
)


#ChildSex

ci_bal_sex <- function(data,idx){
  df <- data[idx, ]
  
  bal_check <- sum((df$School_meal/df$π)*df$ChildSex)
    
  diff <- bal_check/1665 - sum(df$ChildSex)/1665

  return(diff)
  
}
boot_sex <- boot(dataate, ci_bal_sex, R = 1500)
suppressWarnings(
ci_sex <- boot.ci(boot_sex)
)


#black

ci_bal_black <- function(data,idx){
  df <- data[idx, ]
  
  bal_check <- sum((df$School_meal/df$π)*df$black)
    
  diff <- bal_check/1665 - sum(df$black)/1665

  return(diff)
  
}
boot_black <- boot(dataate, ci_bal_black, R = 1500)
suppressWarnings(
ci_black <- boot.ci(boot_black)
)


#mexam

ci_bal_mexam <- function(data,idx){
  df <- data[idx, ]
  
  bal_check <- sum((df$School_meal/df$π)*df$mexam)
    
  diff <- bal_check/1665 - sum(df$mexam)/1665

  return(diff)
  
}
boot_mex <- boot(dataate, ci_bal_mexam, R = 1500)
suppressWarnings(
ci_mex <- boot.ci(boot_mex)
)


#pir200_plus

ci_bal_pir <- function(data,idx){
  df <- data[idx, ]
  
  bal_check <- sum((df$School_meal/df$π)*df$pir200_plus)
    
  diff <- bal_check/1665 - sum(df$pir200_plus)/1665

  return(diff)
  
}
boot_pir <- boot(dataate, ci_bal_pir, R = 1500)
suppressWarnings(
ci_pir <- boot.ci(boot_pir)
)


#WIC

ci_bal_wic <- function(data,idx){
  df <- data[idx, ]
  
  bal_check <- sum((df$School_meal/df$π)*df$WIC)
    
  diff <- bal_check/1665 - sum(df$WIC)/1665

  return(diff)
  
}
boot_wic <- boot(dataate, ci_bal_wic, R = 1500)
suppressWarnings(
ci_wic <- boot.ci(boot_wic)
)


#Food_Stamp

ci_bal_stamp <- function(data,idx){
  df <- data[idx, ]
  
  bal_check <- sum((df$School_meal/df$π)*df$Food_Stamp)
    
  diff <- bal_check/1665 - sum(df$Food_Stamp)/1665

  return(diff)
  
}
boot_stamp <- boot(dataate, ci_bal_stamp, R = 1500)
suppressWarnings(
ci_stamp <- boot.ci(boot_stamp)
)


#fsdchbi

ci_bal_fs <- function(data,idx){
  df <- data[idx, ]
  
  bal_check <- sum((df$School_meal/df$π)*df$fsdchbi)
    
  diff <- bal_check/1665 - sum(df$fsdchbi)/1665

  return(diff)
  
}
boot_fs <- boot(dataate, ci_bal_fs, R = 1500)
suppressWarnings(
ci_fs <- boot.ci(boot_fs)
)


#AnyIns

ci_bal_anyins <- function(data,idx){
  df <- data[idx, ]
  
  bal_check <- sum((df$School_meal/df$π)*df$AnyIns)
    
  diff <- bal_check/1665 - sum(df$AnyIns)/1665

  return(diff)
  
}
boot_anyins <- boot(dataate, ci_bal_anyins, R = 1500)
suppressWarnings(
ci_ins <- boot.ci(boot_anyins)
)


#RefSex

ci_bal_refsex <- function(data,idx){
  df <- data[idx, ]
  
  bal_check <- sum((df$School_meal/df$π)*df$RefSex)
    
  diff <- bal_check/1665 - sum(df$RefSex)/1665

  return(diff)
  
}
boot_refsex <- boot(dataate, ci_bal_refsex, R = 1500)
suppressWarnings(
ci_refsex <- boot.ci(boot_refsex)
)


#RefAge

ci_bal_refage <- function(data,idx){
  df <- data[idx, ]
  
  bal_check <- sum((df$School_meal/df$π)*df$RefAge)
    
  diff <- bal_check/1665 - sum(df$RefAge)/1665

  return(diff)
  
}
boot_refage <- boot(dataate, ci_bal_refage, R = 1500)
suppressWarnings(
ci_refage <- boot.ci(boot_refage)
)

balancing_estimates <- c(boot_age$t0, boot_sex$t0, boot_black$t0, boot_mex$t0, 
                         boot_pir$t0, boot_wic$t0, boot_stamp$t0, boot_fs$t0, 
                         boot_anyins$t0, boot_refsex$t0, boot_refage$t0)

balancing_ci_h <- c(ci_age$percent[5], ci_sex$percent[5], ci_black$percent[5], 
                    ci_mex$percent[5], ci_pir$percent[5], ci_wic$percent[5], 
                    ci_stamp$percent[5], ci_fs$percent[5], ci_ins$percent[5], 
                    ci_refsex$percent[5], ci_refage$percent[5])

balancing_ci_l <- c(ci_age$percent[4], ci_sex$percent[4], ci_black$percent[4], 
                    ci_mex$percent[4], ci_pir$percent[4], ci_wic$percent[4], 
                    ci_stamp$percent[4], ci_fs$percent[4], ci_ins$percent[4], 
                    ci_refsex$percent[4], ci_refage$percent[4])

balancing_scores <- data.frame(balancing_estimates, balancing_ci_l, balancing_ci_h)

row.names(balancing_scores) <- c("age", "ChildSex", "black", "mexam", 
                                 "pir200_plus", "WIC", "Food_Stamp", 
                                 "fsdchbi", "AnyIns", "RefSex", "RefAge")
 
print(balancing_scores)


```

# Causal Effects Using OR Estimator

$\theta^{or}_{ATE} = E[\hat\mu (A=1, X) - \hat\mu(A=0, X)]$

```{r, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)


lm1 <- lm(BMI ~ age + I(age^2) + I(age^3) + ChildSex + black + mexam + 
            pir200_plus + WIC + Food_Stamp + fsdchbi + AnyIns + RefAge, 
          data = subset(datanf, School_meal == 1))
          
lm0 <- lm(BMI ~ age + I(age^2) + I(age^3) + ChildSex + black + mexam + 
            pir200_plus + WIC + Food_Stamp + fsdchbi + AnyIns + RefAge, 
          data = subset(datanf, School_meal == 0))


mu <- function(lm, data){
  lm$coefficients[1] + lm$coefficients[2]*data$age + 
    lm$coefficients[3]*data$age^2 + lm$coefficients[4]*data$age^3 + 
    lm$coefficients[5]*data$ChildSex + lm$coefficients[6]*data$black + 
    lm$coefficients[7]*data$mexam + lm$coefficients[8]*data$pir200_plus + 
    lm$coefficients[9]*data$WIC + lm$coefficients[10]*data$Food_Stamp + 
    lm$coefficients[11]*data$fsdchbi + lm$coefficients[12]*data$AnyIns + 
    lm$coefficients[13]*data$RefAge
}


ate_or <- (sum(mu(lm1,dataate) - mu(lm0,dataate)))/1665


vec_par_or <- c()

for (t in 1:1500){
  
  data1 = data[sample(nrow(datanf), size = 1665, replace = TRUE), ]
  
  lm2 <- lm(BMI ~ age + I(age^2) + I(age^3) + ChildSex + black + mexam + 
              pir200_plus + WIC + Food_Stamp + fsdchbi + AnyIns + RefAge, 
            data = subset(data1, School_meal == 1))
          
  lm3 <- lm(BMI ~ age + I(age^2) + I(age^3) + ChildSex + black + mexam + 
              pir200_plus + WIC + Food_Stamp + fsdchbi + AnyIns + RefAge, 
            data = subset(data1, School_meal == 0))
  
  par_or <- (sum(mu(lm2,dataate)) - sum(mu(lm3,dataate)))/1665
  
  
  vec_par_or <- append(vec_par_or, par_or)
  
  rm(par_or)
  
}

mean_or = mean(vec_par_or)

SE_or = sd(vec_par_or)/sqrt(length(vec_par_or))



```

# Causal Effects Using IPW Estimator

$\theta^{ipw}_{ATE} = E[\frac{A_i}{π(X_i)}Y_i - \frac{1-A_i}{1-π(X_i)}Y_i]$

```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)


ate_ipw <- sum(((dataate$School_meal/dataate$π)*dataate$BMI) - 
                 (((1-dataate$School_meal)/(1-dataate$π))*dataate$BMI))/1665

vec_par_ipw <- c()


for (t in 1:1500){
  data2 = data[sample(nrow(datanf), size = 1665, replace = TRUE), ]
  
  prop_score1 <- glm(School_meal ~ age + I(age^2) + I(age^3) + ChildSex + black 
                     + mexam + pir200_plus + WIC + Food_Stamp + fsdchbi + AnyIns 
                     + RefAge, data = data2, family = "binomial")
  
  dataate$π2 <- predict(prop_score1, dataate, type = "response")
  
  par_ipw <- sum(((dataate$School_meal/dataate$π2)*dataate$BMI) - 
                   (((1-dataate$School_meal)/(1-dataate$π2))*dataate$BMI))/1665
  
  
  vec_par_ipw <- append(vec_par_ipw, par_ipw)
  
  rm(par_ipw)
  
}

mean_ipw = mean(vec_par_ipw)

SE_ipw = sd(vec_par_ipw)/sqrt(length(vec_par_ipw))



```

# Causal Effects Using Hajek Estimator

$\theta^{hajek}_{ATE} = E[\frac{A_i/π(X_i)}{E_n[A/π(X_i)]}Y_i - \frac{(1-A_i)/(1-π(X_i))}{E_n[(1-A_i)/(1-π(X_i))]}Y_i]$

```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

En1 <- sum(dataate$School_meal/dataate$π)/1665

En2 <- sum((1-dataate$School_meal)/(1-dataate$π))/1665

ate_hajek <- sum((((dataate$School_meal/dataate$π)/En1)*dataate$BMI) - 
                   ((((1-dataate$School_meal)/(1-dataate$π))/En2)*dataate$BMI))/1665


vec_par_hajek <- c()


for (t in 1:1500){
  data3 = data[sample(nrow(datanf), size = 1665, replace = TRUE), ]
  
  prop_score2 <- glm(School_meal ~ age + I(age^2) + I(age^3) + ChildSex + black 
                     + mexam + pir200_plus + WIC + Food_Stamp + fsdchbi + AnyIns 
                     + RefAge, data = data3, family = "binomial")
  
  dataate$π3 <- predict(prop_score2, dataate, type = "response")
  
  En1.1 <- sum(dataate$School_meal/dataate$π3)/1665

  En2.1 <- sum((1-dataate$School_meal)/(1-dataate$π3))/1665

  par_hajek <- sum((((dataate$School_meal/dataate$π3)/En1.1)*dataate$BMI) - 
                     ((((1-dataate$School_meal)/(1-dataate$π3))/En2.1)*
                        dataate$BMI))/1665
  
  
  vec_par_hajek <- append(vec_par_hajek, par_hajek)
  
  rm(par_hajek)
  
}

mean_hajek = mean(vec_par_hajek)

SE_hajek = sd(vec_par_hajek)/sqrt(length(vec_par_hajek))


```

# Causal Effects Using Doubly Robust Estimator

$\theta^{dr}_{ATE} = E[\frac{A_i[Y_i- \hat\mu(1,X_i)]}{\hatπ(X_i)} + \hat\mu(1,X_i) - \frac{(1-A_i)[Y_i- \hat\mu(0,X_i)]}{1-\hatπ(X_i)} + \hat\mu(0,X_i) ]$

```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

ate_dr <- sum((dataate$School_meal*(dataate$BMI-mu(lm1,dataate)))/dataate$π + 
                mu(lm1,dataate) - ((1-dataate$School_meal)*
                                     (dataate$BMI-mu(lm0,dataate)))/
                (1-dataate$π) - mu(lm0,dataate))/1665


vec_par_dr <- c()

for (t in 1:1500){
  data4 = data[sample(nrow(datanf), size = 1665, replace = TRUE), ]
  
  lm4 <- lm(BMI ~ age + I(age^2) + I(age^3) + ChildSex + black + mexam + 
              pir200_plus + WIC + Food_Stamp + fsdchbi + AnyIns + RefAge, 
            data = subset(data4, School_meal == 1))
          
  lm5 <- lm(BMI ~ age + I(age^2) + I(age^3) + ChildSex + black + mexam + 
              pir200_plus + WIC + Food_Stamp + fsdchbi + AnyIns + RefAge, 
            data = subset(data4, School_meal == 0))
    
  
  prop_score3 <- glm(School_meal ~ age + I(age^2) + I(age^3) + ChildSex + black 
                     + mexam + pir200_plus + WIC + Food_Stamp + fsdchbi + AnyIns 
                     + RefAge , data = data4, family = "binomial")
  
  dataate$π4 <- predict(prop_score3, dataate, type = "response")

  par_dr <- sum((dataate$School_meal*(dataate$BMI-mu(lm4,dataate)))/dataate$π4 
                + mu(lm4,dataate) - ((1-dataate$School_meal)*
                                       (dataate$BMI-mu(lm5,dataate)))/
                  (1-dataate$π4) - mu(lm5,dataate))/1665
  
  
  vec_par_dr <- append(vec_par_dr, par_dr)
  
  rm(par_dr)
  
}

mean_dr = mean(vec_par_dr)

SE_dr = sd(vec_par_dr)/sqrt(length(vec_par_dr))


```

# Results for OR, IPW, Hajek, DR

```{r}


non_bootstrap_ate <- c(ate_or, ate_ipw, ate_hajek, ate_dr)

bootstrap_ate <- c(mean_or, mean_ipw, mean_hajek, mean_dr)

standard_error <- c(SE_or, SE_ipw, SE_hajek, SE_dr)

ATE_estimates <- data.frame(non_bootstrap_ate, bootstrap_ate, standard_error)

row.names(ATE_estimates) <- c("OR", "IPW", "Hajek", "DR")

print(ATE_estimates)

```

# Matching Estimator with M=3

```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

covmat <- cov(subset(data[4:14]))

meanvec <- colMeans(subset(data[4:14]))

data$mdist <- mahalanobis(subset(data[4:14]), meanvec, covmat)

m.treat <- subset(data, School_meal == 1)

m.control <- subset(data, School_meal == 0)



matched3_y_treat <- c()


new_control <- m.treat[0,]

for (ii in 1:1284) {
  
  m1 <- Closest(m.control$mdist, m.treat$mdist[ii])

  m2 <- Closest(m.control$mdist[!m.control$mdist == m1], m.treat$mdist[ii])

  m3 <- Closest(m.control$mdist[!m.control$mdist %in% c(m1,m2)], m.treat$mdist[ii])
  
  me <- matrix(data = colMeans(m.control[ m.control$mdist == m1 | 
                                            m.control$mdist == m2 | 
                                            m.control$mdist == m3 ,]), 
               ncol = 15, nrow = 1)
  
  colnames(me) = c("X", "BMI", "School_meal", "age", "ChildSex", "black", 
                   "mexam", "pir200_plus", "WIC", "Food_Stamp", "fsdchbi", 
                   "AnyIns", "RefSex", "RefAge", "mdist")
  
  new_control <- rbind(new_control, me)
  
  y1 <- m.control$BMI[m.control$mdist == m1]
  
  y2 <- m.control$BMI[m.control$mdist == m2]
  
  y3 <- m.control$BMI[m.control$mdist == m3]
  
  y <- c(y1,y2,y3)

  matched3_y_treat <- append(matched3_y_treat, mean(y))  
  
}

m.treat$match <- matched3_y_treat


matched3_y_cont <- c()

for (jj in 1:1046) {
  
  m1 <- Closest(m.treat$mdist, m.control$mdist[jj])

  m2 <- Closest(m.treat$mdist[!m.treat$mdist == m1], m.control$mdist[jj])

  m3 <- Closest(m.treat$mdist[!m.treat$mdist %in% c(m1,m2)], m.control$mdist[jj])
  
  y1 <- m.treat$BMI[m.treat$mdist == m1]
  
  y2 <- m.treat$BMI[m.treat$mdist == m2]
  
  y3 <- m.treat$BMI[m.treat$mdist == m3]
  
  y <- c(y1,y2,y3)

  matched3_y_cont <- append(matched3_y_cont, mean(y))  
}

m.control$match <- matched3_y_cont

matched_data <- rbind(m.control, m.treat)

matched_data <- matched_data[order(matched_data$X),]

ate_match3 <- (1/2330)*sum((2*matched_data$School_meal - 1)*
                             (matched_data$BMI - matched_data$match))

ate_match3_bias <- (1/2330)*sum(mu(lm1,matched_data) + 
                                  (matched_data$School_meal *
                                     (matched_data$BMI - mu(lm1, matched_data) 
                                      - matched_data$match)) - 
                                  mu(lm1,matched_data) - 
                                  (ifelse(matched_data$School_meal == 0, 1, 0) 
                                   *(matched_data$BMI - mu(lm1, matched_data) 
                                     - matched_data$match)))



```

# Matching Estimator with M = 6

```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

m.treat <- subset(data, School_meal == 1)

m.control <- subset(data, School_meal == 0)


matched6_y_treat <- c()

new_control <- m.treat[0,]

for (ii in 1:1284) {
  
  m1 <- Closest(m.control$mdist, m.treat$mdist[ii])

  m2 <- Closest(m.control$mdist[!m.control$mdist == m1], m.treat$mdist[ii])

  m3 <- Closest(m.control$mdist[!m.control$mdist %in% c(m1,m2)], 
                m.treat$mdist[ii])
  
  m4 <- Closest(m.control$mdist[!m.control$mdist %in% c(m1,m2,m3)], 
                m.treat$mdist[ii])
  
  m5 <- Closest(m.control$mdist[!m.control$mdist %in% c(m1,m2,m3,m4)], 
                m.treat$mdist[ii])
  
  m6 <- Closest(m.control$mdist[!m.control$mdist %in% c(m1,m2,m3,m4,m5)], 
                m.treat$mdist[ii])
  
  me <- matrix(data = colMeans(m.control[ m.control$mdist == m1 | 
                                            m.control$mdist == m2 | 
                                            m.control$mdist == m3 | 
                                            m.control$mdist == m4 | 
                                            m.control$mdist == m5 | 
                                            m.control$mdist == m6,]), 
               ncol = 15, nrow = 1)
  
  colnames(me) = c("X", "BMI", "School_meal", "age", "ChildSex", "black", 
                   "mexam", "pir200_plus", "WIC", "Food_Stamp", "fsdchbi", 
                   "AnyIns", "RefSex", "RefAge", "mdist")
  
  new_control <- rbind(new_control, me)
  
  y1 <- m.control$BMI[m.control$mdist == m1]
  
  y2 <- m.control$BMI[m.control$mdist == m2]
  
  y3 <- m.control$BMI[m.control$mdist == m3]
  
  y4 <- m.control$BMI[m.control$mdist == m4]
  
  y5 <- m.control$BMI[m.control$mdist == m5]
  
  y6 <- m.control$BMI[m.control$mdist == m6]
  
  
  y <- c(y1,y2,y3,y4,y5,y6)

  matched6_y_treat <- append(matched6_y_treat, mean(y))  
}

m.treat$match <- matched6_y_treat


matched6_y_cont <- c()

for (jj in 1:1046) {
  
  m1 <- Closest(m.treat$mdist, m.control$mdist[jj])

  m2 <- Closest(m.treat$mdist[!m.treat$mdist == m1], m.control$mdist[jj])

  m3 <- Closest(m.treat$mdist[!m.treat$mdist %in% c(m1,m2)], 
                m.control$mdist[jj])
  
  m4 <- Closest(m.treat$mdist[!m.treat$mdist %in% c(m1,m2,m3)], 
                m.control$mdist[jj])
  
  m5 <- Closest(m.treat$mdist[!m.treat$mdist %in% c(m1,m2,m3,m4)], 
                m.control$mdist[jj])
  
  m6 <- Closest(m.treat$mdist[!m.treat$mdist %in% c(m1,m2,m3,m4,m5)], 
                m.control$mdist[jj])
  
  y1 <- m.treat$BMI[m.treat$mdist == m1]
  
  y2 <- m.treat$BMI[m.treat$mdist == m2]
  
  y3 <- m.treat$BMI[m.treat$mdist == m3]
  
  y4 <- m.treat$BMI[m.treat$mdist == m4]
  
  y5 <- m.treat$BMI[m.treat$mdist == m5]
  
  y6 <- m.treat$BMI[m.treat$mdist == m6]
  
  y <- c(y1,y2,y3,y4,y5,y6)

  matched6_y_cont <- append(matched6_y_cont, mean(y))  
}

m.control$match <- matched6_y_cont

matched_data <- rbind(m.control, m.treat)

matched_data <- matched_data[order(matched_data$X),]

ate_match6 <- (1/2330)*sum((2*matched_data$School_meal - 1)*
                             (matched_data$BMI - matched_data$match))

ate_match6_bias <- (1/2330)*sum(mu(lm1,matched_data) + 
                                  (matched_data$School_meal 
                                   *(matched_data$BMI - mu(lm1, matched_data) 
                                     - matched_data$match)) 
                                - mu(lm1,matched_data) 
                                - (ifelse(matched_data$School_meal == 0, 1, 0) 
                                   *(matched_data$BMI - mu(lm1, matched_data) 
                                     - matched_data$match)))



```

# Matching Estimator with M = 10

```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

m.treat <- subset(data, School_meal == 1)

m.control <- subset(data, School_meal == 0)



matched10_y_treat <- c()

new_control <- m.treat[0,]

for (ii in 1:1284) {
  
  m1 <- Closest(m.control$mdist, m.treat$mdist[ii])

  m2 <- Closest(m.control$mdist[!m.control$mdist == m1], m.treat$mdist[ii])

  m3 <- Closest(m.control$mdist[!m.control$mdist %in% c(m1,m2)], 
                m.treat$mdist[ii])
  
  m4 <- Closest(m.control$mdist[!m.control$mdist %in% c(m1,m2,m3)], 
                m.treat$mdist[ii])
  
  m5 <- Closest(m.control$mdist[!m.control$mdist %in% c(m1,m2,m3,m4)], 
                m.treat$mdist[ii])
  
  m6 <- Closest(m.control$mdist[!m.control$mdist %in% c(m1,m2,m3,m4,m5)], 
                m.treat$mdist[ii])
  
  m7 <- Closest(m.control$mdist[!m.control$mdist %in% c(m1,m2,m3,m4,m5,m6)], 
                m.treat$mdist[ii])
  
  m8 <- Closest(m.control$mdist[!m.control$mdist %in% c(m1,m2,m3,m4,m5,m6,m7)], 
                m.treat$mdist[ii])
  
  m9 <- Closest(m.control$mdist[!m.control$mdist %in% 
                                  c(m1,m2,m3,m4,m5,m6,m7,m8)], m.treat$mdist[ii])
  
  m10 <- Closest(m.control$mdist[!m.control$mdist 
                                 %in% c(m1,m2,m3,m4,m5,m6,m7,m8,m9)], 
                 m.treat$mdist[ii])
  
  me <- matrix(data = colMeans(m.control[ m.control$mdist == m1 | 
                                            m.control$mdist == m2 | 
                                            m.control$mdist == m3 | 
                                            m.control$mdist == m4 | 
                                            m.control$mdist == m5 | 
                                            m.control$mdist == m6 | 
                                            m.control$mdist == m7 |
                                            m.control$mdist == m8 | 
                                            m.control$mdist == m9 | 
                                            m.control$mdist == m10 ,]), 
               ncol = 15, nrow = 1)
  
  colnames(me) = c("X", "BMI", "School_meal", "age", "ChildSex", "black", 
                   "mexam", "pir200_plus", "WIC", "Food_Stamp", "fsdchbi", 
                   "AnyIns", "RefSex", "RefAge", "mdist")
  
  new_control <- rbind(new_control, me)
  
  y1 <- m.control$BMI[m.control$mdist == m1]
  
  y2 <- m.control$BMI[m.control$mdist == m2]
  
  y3 <- m.control$BMI[m.control$mdist == m3]
  
  y4 <- m.control$BMI[m.control$mdist == m4]
  
  y5 <- m.control$BMI[m.control$mdist == m5]
  
  y6 <- m.control$BMI[m.control$mdist == m6]
  
  y7 <- m.control$BMI[m.control$mdist == m7]
  
  y8 <- m.control$BMI[m.control$mdist == m8]
  
  y9 <- m.control$BMI[m.control$mdist == m9]
  
  y10 <- m.control$BMI[m.control$mdist == m10]
  
  
  y <- c(y1,y2,y3,y4,y5,y6,y7,y8,y9,y10)

  matched10_y_treat <- append(matched10_y_treat, mean(y))  
}

m.treat$match <- matched10_y_treat


matched10_y_cont <- c()

for (jj in 1:1046) {
  
  m1 <- Closest(m.treat$mdist, m.control$mdist[jj])

  m2 <- Closest(m.treat$mdist[!m.treat$mdist == m1], m.control$mdist[jj])

  m3 <- Closest(m.treat$mdist[!m.treat$mdist %in% c(m1,m2)], 
                m.control$mdist[jj])
  
  m4 <- Closest(m.treat$mdist[!m.treat$mdist %in% c(m1,m2,m3)],
                m.control$mdist[jj])
  
  m5 <- Closest(m.treat$mdist[!m.treat$mdist %in% c(m1,m2,m3,m4)], 
                m.control$mdist[jj])
  
  m6 <- Closest(m.treat$mdist[!m.treat$mdist %in% c(m1,m2,m3,m4,m5)],
                m.control$mdist[jj])
  
  m7 <- Closest(m.treat$mdist[!m.treat$mdist %in% c(m1,m2,m3,m4,m5,m6)], 
                m.control$mdist[jj])
  
  m8 <- Closest(m.treat$mdist[!m.treat$mdist %in% c(m1,m2,m3,m4,m5,m6,m7)], 
                m.control$mdist[jj])
  
  m9 <- Closest(m.treat$mdist[!m.treat$mdist %in% c(m1,m2,m3,m4,m5,m6,m7,m8)], 
                m.control$mdist[jj])
  
  m10 <- Closest(m.treat$mdist[!m.treat$mdist 
                               %in% c(m1,m2,m3,m4,m5,m6,m7,m8,m9)], 
                 m.control$mdist[jj])
  
  y1 <- m.treat$BMI[m.treat$mdist == m1]
  
  y2 <- m.treat$BMI[m.treat$mdist == m2]
  
  y3 <- m.treat$BMI[m.treat$mdist == m3]
  
  y4 <- m.treat$BMI[m.treat$mdist == m4]
  
  y5 <- m.treat$BMI[m.treat$mdist == m5]
  
  y6 <- m.treat$BMI[m.treat$mdist == m6]
  
  y7 <- m.treat$BMI[m.treat$mdist == m7]
  
  y8 <- m.treat$BMI[m.treat$mdist == m8]
  
  y9 <- m.treat$BMI[m.treat$mdist == m9]
  
  y10 <- m.treat$BMI[m.treat$mdist == m10]
  
  y <- c(y1,y2,y3,y4,y5,y6,y7,y8,y9,y10)

  matched10_y_cont <- append(matched10_y_cont, mean(y))  
}

m.control$match <- matched10_y_cont

matched_data <- rbind(m.control, m.treat)

matched_data <- matched_data[order(matched_data$X),]

ate_match10 <- (1/2330)*sum((2*matched_data$School_meal - 1)
                            *(matched_data$BMI - matched_data$match))

ate_match10_bias <- (1/2330)*sum(mu(lm1,matched_data) + 
                                   (matched_data$School_meal 
                                    *(matched_data$BMI - mu(lm1, matched_data)
                                      - matched_data$match)) -
                                   mu(lm1,matched_data) -
                                   (ifelse(matched_data$School_meal == 0, 1, 0)
                                    *(matched_data$BMI - mu(lm1, matched_data)
                                      - matched_data$match)))

```

# Matching Results

```{r}
match_ate <- c(ate_match3, ate_match6, ate_match10)

bias_corrected_ate <- c(ate_match3_bias, ate_match6_bias, ate_match10_bias)

MATCH_estimates <- data.frame(match_ate, bias_corrected_ate)

row.names(MATCH_estimates) <- c("M=3", "M=6", "M=10")

print(MATCH_estimates)

```

# Matching Distribuition

```{r}
covariates <- c("X", "BMI", "School_meal", "age", "ChildSex", "black", 
                "mexam", "pir200_plus", "WIC", "Food_Stamp", "fsdchbi", 
                "AnyIns", "RefSex", "RefAge", "mdist")

titles <- c("control_pre", "treat", "control_post")

for (i in 4:15){
  par(mfrow = c(1,3))
  hist(matched_data[,i][data$School_meal == 0], xlab = covariates[i], 
       main = titles[1])
  abline(v=mean(matched_data[,i][data$School_meal == 0]), col = "orange")

  hist(matched_data[,i][data$School_meal == 1], xlab = covariates[i],
       main = titles[2])
  abline(v=mean(matched_data[,i][data$School_meal == 1]), col = "orange")
  
  hist(new_control[,i], xlab = covariates[i], main = titles[3])
  abline(v=mean(new_control[,i]), col = "orange")
}


```
